---
title: "Quarto 1"
author: "Peter Baumgartner"
format: html
execute: 
  echo: false
---


```{r}
suppressPackageStartupMessages(library(tidyverse))
library(palmerpenguins)
```


```{r}
penguins
```


## Result from my Positron Assistent

The question was: 

> Using R and the tidyverse package, create a beautiful graphic using the penguins data from the palmerpenguins package.

```{r}
library(tidyverse)
library(palmerpenguins)

ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm, color = species)) +
  geom_point(aes(shape = species), size = 3, alpha = 0.8) +
  geom_smooth(method = "lm", se = FALSE, linewidth = 1) +
  labs(
    title = "Penguin Bill Dimensions by Species",
    subtitle = "Palmer Archipelago LTER Penguins",
    x = "Bill Length (mm)",
    y = "Bill Depth (mm)",
    color = "Species",
    shape = "Species",
    caption = "Data from palmerpenguins package"
  ) +
  scale_color_manual(
    values = c(
      "Adelie" = "#ff6f00",
      "Chinstrap" = "#c75bcb",
      "Gentoo" = "#067476"
    )
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
    plot.subtitle = element_text(size = 12, hjust = 0.5, color = "gray40"),
    legend.position = "bottom",
    panel.grid.minor = element_blank(),
    plot.caption = element_text(color = "gray50", size = 9)
  )
```

The scatter plot shows how bill dimensions differ across the three penguin species, with distinct colors and shapes for each species. Linear regression lines help visualize the relationship within each species. The plot uses a clean minimal theme with custom colors and thoughtful formatting.

## Result from the tutorial example


```{r}
theme_custom <- theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", size = 16, hjust = 0.5),
    plot.subtitle = element_text(size = 12, hjust = 0.5),
    legend.position = "right",
    panel.grid.major = element_line(color = "grey80"),
    panel.grid.minor = element_blank()
  )

penguins |>
  drop_na() |>
  ggplot(aes(x = flipper_length_mm, y = body_mass_g, color = species)) +
  geom_point(alpha = 0.8, size = 3) +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, linetype = "dashed") +
  scale_color_brewer(palette = "Dark2") +
  labs(
    title = "Penguin Flipper Length vs Body Mass",
    subtitle = "Species comparison from Palmer Station, Antarctica",
    x = "Flipper Length (mm)",
    y = "Body Mass (g)",
    color = "Species",
    caption = "Data from the palmerpenguins package"
  ) +
  theme_custom
```


